\documentclass[13pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Fixes font mapping issues
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Colors
\definecolor{primary}{RGB}{0, 73, 135}

% Formatting
\titleformat{\section}{\Large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \textit{#4} \vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{4pt}\item
    \textbf{#1} \hfill \textit{#2} \vspace{-4pt}
}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Aman Yadav}} \\ \vspace{4pt}
    {\large Final Year B.Sc. (Hons.) Biotechnology with Research} \\ \vspace{2pt}
    \small Delhi (NCR) $|$ +91-9971821769 $|$ \href{mailto:aman0001yadavdu@gmail.com}{\color{primary}aman0001yadavdu@gmail.com} \\
    \href{https://www.linkedin.com/in/aman-yadav-4000-k/}{\color{primary}LinkedIn: aman-yadav-4000-k} $|$
    \href{https://github.com/aman0001yadavdu-bit}{\color{primary}GitHub: aman0001yadavdu-bit}
\end{center}

% Education
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
        {Gautam Buddha University (GBU)}{Greater Noida, India}
        {B.Sc. (Hons.) Biotechnology with Research}{Expected 2026}
        \begin{itemize}
            \resumeItem{Focus on Bioinformatics, Data Analysis, and Computational Biology.}
            \resumeItem{Gained foundational wet lab skills including Plasmid Isolation, PCR, and DNA Extraction.}
        \end{itemize}
\end{itemize}

% Technical Skills
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Programming \& Web:} Python, R, HTML5, CSS, Backend Development
    \item \textbf{Bioinformatics \& Data Science:} Single-Cell RNA-Seq (scRNA-Seq) Analysis, Bulk RNA-Seq Analysis, Machine Learning, Differential Gene Expression (DEG), Computational Biology
    \item \textbf{Tools \& Software:} RStudio, AutoDock, PyMOL, OpenBabel, Seurat, Harmony, Scanpy
    \item \textbf{Operating Systems:} Linux, Fedora, Ubuntu, Windows
    \item \textbf{Wet Lab:} Plasmid Isolation, PCR, DNA Extraction
\end{itemize}

% Experience
\section{Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
        {Research Intern -- Computational Biology}{Summer 2025}
        {Gautam Buddha University}{}
        \begin{itemize}
            \resumeItem{Project: \textit{Screening of potential dual inhibitors of SGLT1 and SGLT2 in diabetes mellitus therapy}.}
            \resumeItem{Applied computational biology and bioinformatics techniques utilizing AutoDock, PyMOL, and OpenBabel.}
            \resumeItem{Developed scientific thinking and analytical skills for target-based drug discovery applications.}
        \end{itemize}
    \resumeSubheading
        {Freelance Web Developer}{2025 -- 2026}
        {The Food Adda}{}
        \begin{itemize}
            \resumeItem{Designed and developed a responsive cafeteria website using HTML5 and CSS (\href{https://aman0001yadavdu-bit.github.io/The-Food-Adda-Website/}{Portfolio Link}).}
            \resumeItem{Gained hands-on experience in frontend development and freelance client delivery.}
        \end{itemize}
\end{itemize}

% Academic Projects
\section{Academic Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeProjectHeading
        {Screening of DEG for Parkinson's Disease (scRNA-Seq)}{8th Semester Major Project}
        \begin{itemize}
            \resumeItem{Performed single-cell RNA-Seq data analysis (leveraging packages like Seurat and Harmony) on Parkinson's disease datasets (e.g., GSE202210) using RStudio.}
            \resumeItem{Identified differentially expressed genes and utilized Linux (Ubuntu/Fedora) for high-performance computing.}
            \resumeItem{Source code available on \href{https://github.com/aman0001yadavdu-bit}{GitHub}.}
        \end{itemize}
    \resumeProjectHeading
        {Screening of Significant DEG for Parkinson's Disease}{7th Semester Minor Project}
        \begin{itemize}
            \resumeItem{Analyzed bulk RNA-Seq datasets utilizing Python programming (Scanpy, etc.) to identify target genes.}
            \resumeItem{Applied machine learning algorithms to evaluate and cluster differential gene expression profiles.}
            \resumeItem{Source code available on \href{https://github.com/aman0001yadavdu-bit}{GitHub}.}
        \end{itemize}
    \resumeProjectHeading
        {Personal Portfolio Website}{Independent Project}
        \begin{itemize}
            \resumeItem{Developed a digital web portfolio to showcase bioinformatics research, web development projects, and technical skills.}
        \end{itemize}
\end{itemize}

% Certifications
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Python for Data Science, AI \& Development}
    \item \textbf{Machine Learning with Python}
\end{itemize}

% Conferences \& Workshops
\section{Conferences \& Workshops}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{2nd IEEE International Conference on Cognitive Computing in Engineering, Communications, Sciences and Biomedical Health Informatics (IC3ECSBHI-2026):} Attended and Volunteered (Student Co-ordinator, Transport Team Member).
    \item \textbf{International Conference on Structural Biology and Drug Discovery (ICSBDD):} Attended and Volunteered (Discipline Committee Member at University School of Biotechnology, GBU).
    \item \textbf{Protecting Neurodegeneration: Hands-on Training on Cell-Based Neurotoxicity Analysis:} Workshop organized by Amity Centre of Nanomedicine, Amity University.
    \item \textbf{Career Counselling for Biotechnology Students:} Workshop organized by University School of Biotechnology, GBU.
\end{itemize}

\end{document}
